Singapore's Public Housing Affordability

### 2023-12-11 datastory.qmd
Update

According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue. The table below provides an outline of the housing prices in Singapore. Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.

@@

<div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
  <iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
</div>

### Why such analysis is important?

@@

### References

>>>>

According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue. The table above provides an outline of the housing prices in Singapore. Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.

@@

::: {style="display: flex; justify-content: center; align-items: center; overflow: hidden;"}
<iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
</iframe>
:::

### Conclusion: Why such analysis is important?

@@

<p>
